```{r}
library(tidyverse)
library(lubridate)
library(stringr)
library(forcats)
```

```{r}
lacation<-read_csv("Nice_Ride_2017_Station_Locations.csv")
season<-read_csv("Nice_ride_trip_history_2017_season.csv")
```

```{r}
lacation$`Start station number` <- lacation$`Number`
lacation$Number <- NULL
newdata <- full_join(season,lacation,by = "Start station number")
head(newdata)
```
```{r}
seasonstring<-season%>%
select("Account type")%>%
```

```{r}
seasonstring<-str_detect(seasonstring, "M")
```


```{r}
season$`Account` <- season$`Account type`
season$`Account type` <- NULL
relig_summary <- season %>%
  group_by(Account) %>%
  summarise(sec = mean(`Total duration (Seconds)`,secount = count(`Total duration (Seconds)`)))

ggplot(relig_summary, aes(sec, Account)) + geom_point()
```

```{r}
season$`Start` <- season$`Start date`
season$'Start date' <- NULL
```



```{r}
popmonth <- season %>%
  group_by(Month) %>%
  summarise(total=n())
```

```{r}
ggplot(data = popmonth) +
  geom_bar(mapping = aes(x = Month, y = total), stat = "identity")
```

```{r}
popdate <- season %>%
  group_by(Day) %>%
  summarise(all=n())%>%
  arrange(desc(Day))
```

```{r}
ggplot(data = popdate) + 
  geom_point(mapping = aes(x = Day, y = all))


```

Question 1: Do casual member? tend to rent the bike longer?

Finfding: Absoulutely, as you can see from the chart, "Casual" members rent the bikes four times longer than the members, which make sense, because onlypeople who are very into biking will become the bike, which means most of them probably have their own bikes already.


Question 2: Which month is thier most profitable period vs the least profitable period.(By comparing the duration of the retals)


Finding: July is probably the most profitable month for the rental company; whereas, there aren't many people rent the bike on November. From this analysis, I would be able to know that summer is the season for biking, and winter is not. The rental company can come up more activities in the winter to attract their members coming over during the winter season.


Question 3: Similiar to question 2, I would like to know what date is the most popular day for biking.

Finding: From the chart I made on the above, I would made the conclusion that people are not very persistent of what they are doing, which is the reason why many failed on losing weight. From the chart, I am able to tell that the first couple days bikers were very active, while days after the activism dramatically went down. This cycle came up over and over again. So I would assume that bikers arent very persistent, similar to people who wanted to drop their weight tended to work very hard for the first couple days, then wanted to take a break after that.



What did I do for the team: Individual work, asked for instructions clearence, check the format before submitting the group work.